Survivable Set Connectivity

### 2015-05-10 draft.tex
added intuitive exaplanation

@@

\section{Conclusion}

\subsection{Open Problems}

>>>>

\subsection{Algorithm Idea}

Here, we provide an intuitive explanation of the algorithm as well as the main motivations for each procedure. Of course, we will revist these ideas in the analysis.

After running the linear program, we rescale $x$ to $x'$ by $\frac{4}{k}$ to ensure we have a flow of at least $4$ in each pair $(S_i, T_i)$. This flow of $4$ will correspond to a flow of $4$ on the R\"{a}cke trees.

The RoundGKR algorithm is the main tool used for our rounding scheme. RoundGKR guarantees find paths on trees which avoid edges will be found with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow. We repeat this $\tau' = O(\log n)$ times to assure a constant probability.

We can only run RoundGKR on trees. We introduce R\"{a}cke trees specifically for this purpose. We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}). Each flow path will go up the tree to some ancestor $v$ and then back down to a leaf. One such path might be found when $v$ gets marked. One path will go to $s_i'$ and one to $t_i'$.

Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoinding some edges. If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$. We scale the capacities by $2^{q+1}$ in order to search for the flow value. We only scale with probabilities $\dfrac{4}{2^q}$ so our costs does not increase by more than $O(\log n)$. Figure~\ref{fig:roundgkronnode} shows how a flow path might be found.

@@
